A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2019-01-08 doc/large_strain.tex
mention MPI details and add more info on SIMD

Note that the SIMD vectorization
{\color{red}
in \texttt{deal.II} \cite{dealII90}
}
is applied at the finite element level, i.e. the matrix-free operator is applied simultaneously on several elements (called ``blocks'').
{\color{red}
For a given quadrature point, we simultaneously perform tensor evaluations and contractions on all elements. This is achieved using templated number types within the \textit{Tensor} class of the \texttt{deal.II} library.
\textit{FEEvaluation} class already provides all the necessary contraction (such as $\overline{\grad^s} \gz N_i : \boldsymbol{\mathcal{C}}\gz g_s$) to implement the three algorithms proposed above.
Thanks to the object oriented design of the \texttt{deal.II} library, the core of those matrix-free algorithms can be implemented in only a handful of lines.
For more information about the implementation details and performance analysis (????), see \cite{kronbichler12}.
}

>>>>

Note that the SIMD vectorization
{\color{red}
in \texttt{deal.II} \cite{dealII90}
}
is applied at the finite element level, i.e. the matrix-free operator is applied simultaneously on several elements (called ``blocks'').
{\color{red}
For a given quadrature point, we simultaneously perform tensor evaluations and contractions on all elements.
For example, deformation gradient $\gz F = \gz I + \Grad \, \overline{\gz u^h}$ (second order tensor) is evaluated at the specific quadrature point of all elements within the ``block''.
This is achieved using templated number types within the \textit{Tensor} class of the \texttt{deal.II} library.
In particular, \texttt{deal.II} provides the \textit{VectorizedArray} templated generic class that defines a unified interface to a vectorized data type.
The core of the sum factorization algorithms is provided by
\textit{FEEvaluation} class, that already supports all the necessary contraction (such as $\overline{\grad^s} \gz N_i : \boldsymbol{\mathcal{C}}\gz g_s$) to implement the three algorithms proposed above.
Thanks to the object oriented design of the \texttt{deal.II} library, the core of those matrix-free algorithms can be implemented in only a handful of lines.
Distributed memory MPI parallelization of matrix-free operators is done using the standard domain decomposition technique, where each MPI process is responsible for applying the operator only on the so called locally owned elements.
For more information about the implementation details of sum factorization techniques in deal.II and their performance analysis (????), see \cite{kronbichler12}.
}
